PropOcData2

### 2021-08-17 R/PropOc Data 3D.Rmd
Added cumulative Density, 50 percentile and plots for mean 50 perecentile density per condition

countDataClean2<-rawPropOcDataClean %>% group_by(SampleCode, source, Distance) %>% summarize(count = n()) %>% filter(count<1000) %>%ungroup() %>% group_by(SampleCode) %>% summarise(MisingTotal = n()*1000-sum(count),TotalMedian = median(count), Mean = mean(count)) %>% mutate(MissingPercent = (1000-Mean)/1000)
#it got a little better, but not that much...
#####
#How much of it is outside the ideal boundaries?

CheckBenchmark<-function(benchmark){
CheckPropOc<-rawPropOcDataClean %>% filter(PropOc>benchmark|PropOc<0)
percentInbound<-length(CheckPropOc$SampleCode)/length(rawPropOcDataClean$SampleCode)*100
return(percentInbound)}

CheckBenchmark(1)

ggplot()+
  geom_jitter(data = countData,aes(x=Distance,y=X, color = source ),size=4, height= .1)+
  #labs(title ="title")+
  #scale_y_log10(breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
  theme_cowplot()+
  theme(plot.title = element_text(hjust = 0.5))

GetHistograms<-function(sample){

data<-propOcData%>% filter(PropOc <1.02) %>% group_by(Distance, source) 
  dataList<-group_split(data)#split data fram into a list of dataframes with a single distance and from a single source
  histogramList<-map(dataList, HistogramDistance)#run the function on each item of the list created at the top
  output<-bind_rows(histogramList) #go back to a single dataframe 
  return(output)
}

HistogramDistance <- function(df) {
  #histogram<- hist(df$PropOc) 
  histogram<- hist(df$PropOc, breaks = seq.int(0,1.02,.01)) 
  #histogram<- hist(df$PropOc, breaks = c(0,lseq(.001,1.03,100)))
  #histogram<- hist(df$PropOc, breaks = c(0,lseq(.0001,1.03,100)))
  output<-data.frame(histogram$mids,histogram$counts, histogram$density)
  colnames(output)<-c("Value", "Frequency", "Density")
  output<-output %>% mutate(Distance = df$Distance[[1]]) %>% filter(!Frequency==0)
  output<-output %>% mutate(Source = df$source[[1]]) 
  return(output)
}

testReadPropOc<-ReadPropOc("mono_d1_01") #this is using seq(.0001,1.03,100)))
testReadPropOc1<-ReadPropOc("mono_d1_01") #this is using seq(.001,1.03,100)))
testReadPropOc2<-ReadPropOc("mono_d1_01") #this is using seq.int(0,1.02,.01)) 
testReadPropOc3<-ReadPropOc("mono_d1_01") #this is without specifying breaks

testReadPropOcLaptop<-ReadPropOc("mono_d1_01Laptop")

testrawPropOcData<-read.csv(paste0("/Volumes/raw_data/Confocal/Carolyn/2020/Chronic wounds/PropOc Data/", "mono_d1_01",".csv"),header = T)

@@

```{r Original Whole PropOc frequency functions from mBio Paper}
GetAllHistPropOc <- function(df, timepoint){
  data.GG<-GetHistPropOc(df, timepoint, "finalGG")
  data.RG<-GetHistPropOc(df, timepoint, "finalRG")
  data.RR<-GetHistPropOc(df, timepoint, "finalRR")
  data.GR<-GetHistPropOc(df, timepoint, "finalGR")
  allData<- bind_rows(data.GG,data.RR,data.RG,data.GR)
return(allData)
}

@@

```{r Whole PropOc frequency Figures}
PlotAllPropOcData <- function(df, relation ) {
  ggplot()+ 
    geom_point(data = df %>% filter(Source == relation),aes(x=Value,y=Frequency, color = Distance),size=2)+
    scale_y_log10( breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
    #scale_x_log10( breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
    #labs(title =paste( relation, timepoint))+
    #scale_color_viridis(option = "D")+
    scale_color_gradientn(colours = rainbow(5))+
    xlim(0,1)+
    theme_cowplot()+
    theme(plot.title = element_text(hjust = 0.5))
  #name<-paste0(relation, ".hour", timepoint,".png")
  #ggsave(paste0(name),plot = plot, width = 17, height = 10)
}

@@

```{r Whole PropOc Data wrangling}
#So, I think the first thing to do would be to get a "mode", or the highest value for frequency of proportional occupancy per distance.
#at this point I can see at least if the zone of interest is the same for every sample.

@@

```{r Whole Prop Freq Figures}
PlotMaxDensities <- function(df) {
  ggplot()+
    geom_jitter(data = df,aes(y=Value, color=Density,x = Distance, shape = Sample),size=2)+
    labs(title ="Maximum Density")+
    scale_y_log10(breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
    #scale_x_log10(breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
    facet_wrap( ~ Source, ncol = 2)+
    scale_color_gradientn(colours = rainbow(5))+
    scale_shape_manual(values=c(0,1,2, 15,16,17))+
    theme_cowplot()+
    theme(plot.title = element_text(hjust = 0.5))
}
PlotMaxDensities(allDensities)
PlotMaxDensities(allDensitiesFunctions %>% filter(Source=="finalRG"))
PlotMaxDensities(allDensitiesLog)
PlotMaxDensities(allDensitiesLog2)
```
#Calculating 50 percentile density.
```{r death curves Functions and data}
getDeathCurve<-function(df){
  totalFrequency = sum(df$Frequency)
  currentFrequency = 0
  for (i in 1 : nrow(df)){
    addedFrequency<-totalFrequency-currentFrequency
    df[i,6]<-addedFrequency
    currentFrequency = currentFrequency+df[i,2]
  }
  colnames(df)<-c("Value","Frequency","Density", "Distance", "Source","Decay")
  df<-df %>% mutate (normDecay = 100*(Decay - min(Decay)) / (max(Decay) - min(Decay)))
  return(df)
  }
processData<-function(df){
  allData<-df %>% group_by(Distance, Source)
  yas<- group_split(allData)
  mappedData<-map(yas, getDeathCurve)
  boundData<-bind_rows(mappedData)
}
GetPercentiles<-function(histograms){
  histogramNames<- c("wt1.1","wt2.1","wt3.1","mut1.1","mut2.1","mut3.1")
  mappedDensities<-map(histograms,processData)
  namedMappedDensities<-map2(mappedDensities, histogramNames, ~.x %>% mutate(Sample = .y))
  allDensities<-bind_rows(namedMappedDensities)
  allDensities<-allDensities %>% ungroup() %>% 
    mutate(Strain = recode(allDensities$Sample, wt1.1="wt",wt2.1="wt",wt3.1="wt",mut1.1="mut",mut2.1="mut",mut3.1="mut"))
return(allDensities)}

@@

allDeathCurvesLog2midAbsStats<-allDeathCurvesLog2midAbsStats%>% mutate(Relation = recode(Source, "finalGG" = "Pa->Pa","finalRG" = "Sa->Pa","finalRR" = "Sa->Sa","finalGR" = "Pa->Sa"))
ggplot()+#log transform
  geom_pointrange(data = allDeathCurvesLog2midAbsStats,aes(x = Distance,y=meanLogValue,ymax=meanLogValue+sdLogValue,ymin=meanLogValue-sdLogValue, color=Strain),size=.5)+
  facet_wrap( ~ Relation, ncol = 2)+
  scale_color_grey(name = "Strain", labels = c( "HQNO-","Wild Type"))+  
  theme_cowplot()+
  theme(plot.title = element_text(hjust = 0.5))
```
#Enrichment (distance at highest proportional occupancy)
```{r Enrichment}
#find the max proportional occupancy value from the 50 percentile

allDeathCurvesLog2midAbsEnrichment<- allDeathCurvesLog2midAbs %>% group_by(Sample, Source)%>%select(Value, Distance, Source,Sample, Strain, Percentile50) %>% mutate(Enrichment = max(Value)) %>%
  mutate(EnrichmentCh = ifelse(Enrichment == Value, 1, 0 )) %>% filter(EnrichmentCh==1) %>% mutate(DoubledValues = sum(EnrichmentCh)) %>% ungroup()#find max

@@

#That looks like a lot of the values are just at 0.5 distance, which I dont really care, I can make another argument about direct contact, so I'll filter those out...
allDeathCurvesLog2midAbsEnrichment2<- allDeathCurvesLog2midAbs %>% filter(!Distance ==0.5)%>% 
  group_by(Sample, Source) %>% select(Value, Distance, Source,Sample, Strain, Percentile50) %>% mutate(Enrichment = max(Value)) %>%
  mutate(EnrichmentCh = ifelse(Enrichment == Value, 1, 0 )) %>% filter(EnrichmentCh==1) %>% mutate(DoubledValues = sum(EnrichmentCh)) %>% ungroup()#find max

>>>>

countDataClean2<-rawPropOcDataClean %>% group_by(SampleCode, source, Distance) %>% summarize(count = n()) %>% filter(count<1000) %>%ungroup() %>% group_by(SampleCode) %>% summarise(MisingTotal = n()*1000-sum(count),TotalMedian = median(count), Mean = mean(count)) %>% mutate(MissingPercent = (1000-Mean)/1000)
#it got a little better, but not that much...
#####
#What are the observations missing?
#####
countDistancesALL<-rawPropOcDataClean %>% group_by(SampleCode,Condition, source,Distance) %>% summarise(count = n()) %>% ungroup() %>%group_by(Condition) %>%  mutate(difference = max(count)- count)

countDistancesALLwt<- countDistancesALL %>% filter(Condition=="wt")
countDistancesALLpqsL<- countDistancesALL %>% filter(Condition=="pqsL")

ggplot()+
  geom_point(data = countDistancesALLpqsL,aes(x=Distance,y=difference, shape = source, color = SampleCode),size=4)+
  labs(title ="Prop Oc Analysis Sampling missing by Source and Distance(Original Run")+
  facet_grid(.~source)+
  theme_cowplot()+
  theme(plot.title = element_text(hjust = 0.5))
#####
#How much of it is outside the 0 - 1 range?
#####
CheckBenchmark<-function(benchmark){
CheckPropOc<-rawPropOcDataClean %>% filter(PropOc>benchmark|PropOc<0)
#CheckPropOc<-rawPropOcData %>% filter(PropOc<0)
percentInbound<-length(CheckPropOc$SampleCode)/length(rawPropOcDataClean$SampleCode)*100
return(percentInbound)}

CheckBenchmark(1.05)
CheckBenchmark(1.1)
CheckBenchmark(1.2)
CheckBenchmark(1.3)
CheckBenchmark(1.4)
CheckBenchmark(1.5)
CheckBenchmark(1.6)
CheckBenchmark(1.7)
CheckBenchmark(1.8)
CheckBenchmark(1.9)

#the data outside the range should be primarily at really short distances, since this is where the calculation of voxels in the surrounding and sphere of potentially ocuppied space is the largest  
#I think 1.05 is a good benchmark to observe this trend:
CheckPropOc<-rawPropOcDataClean %>% filter(PropOc>1.5|PropOc<0)

ggplot()+
  geom_jitter(data = CheckPropOc %>% filter(!source == "finalRR") %>% filter(!source == "finalGG") %>% filter(PropOc<1000),aes(x=Distance,y=PropOc, color = source ),size=2, height= .1)+
  #labs(title ="title")+
  scale_y_log10(breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
  theme_cowplot()+
  theme(plot.title = element_text(hjust = 0.5))

blah<-CheckPropOc %>% filter(!PropOc<0) %>% group_by(Distance) %>% summarise(counts = n())
ggplot()+
  geom_point(data = blah,aes(x=Distance,y=counts),size=4)+
  scale_y_log10(breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
  theme_cowplot()+
  theme(plot.title = element_text(hjust = 0.5))

#seems like the data outside the boundaries certainly tends to be at low distances, but the values themselves increase with distance
#####
#Add New varaible to the data frame capping the value pf propOc to 1

rawPropOcDataClean$PropOc1= rawPropOcDataClean$PropOc
rawPropOcDataClean$PropOc1[rawPropOcDataClean$PropOc1>1] = 1
rawPropOcDataClean$PropOc1[rawPropOcDataClean$PropOc1<0] = 0
#make new data frame for downstream analysis
PropOcDataFiltered<-rawPropOcDataClean %>% filter(PropOc<1.5) %>% filter(PropOc>=0)

GetHistograms<-function(inputData){
data<-inputData%>% group_by(SampleCode,Distance, source) 
  dataList<-group_split(data)#split data fram into a list of dataframes with a single distance and from a single source
  histogramList<-map(dataList, HistogramDistance)#run the function on each item of the list created at the top
  output<-bind_rows(histogramList) #go back to a single dataframe 
  return(output)
}
HistogramDistance <- function(df) {
  #histogram<- hist(df$PropOc) 
  histogram<- hist(df$PropOc1, breaks = seq.int(0,1,.01)) 
  #histogram<- hist(df$PropOc, breaks = c(0,lseq(.001,1.03,100)))
  #histogram<- hist(df$PropOc, breaks = c(0,lseq(.0001,1.03,100)))
  output<-data.frame(histogram$mids,histogram$counts, histogram$density)
  colnames(output)<-c("Value", "Frequency", "Density")
  output<-output %>% mutate(Distance = df$Distance[[1]]) %>% filter(!Frequency==0)
  output<-output %>% mutate(Source = df$source[[1]])
  output<-output %>% mutate(Sample = df$SampleCode[[1]])
  return(output)
}
#Run histograms for data
propOcHistogramData<-GetHistograms(PropOcDataFiltered)#from here what matters is the density since it is freq/total*#ofbins
propOcHistogramData<-propOcHistogramData %>% group_by(Sample, Source, Distance) %>% mutate(count = sum(Frequency), NormDensity = Density/100) %>% ungroup()

#plot distributions
PlotAllPropOcData <- function(sample ) {
  ggplot()+ 
    geom_point(data = propOcHistogramData %>% filter(Sample ==sample),aes(x=Value,y=NormDensity, color = Distance),size=2)+
    scale_y_log10( breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
    scale_color_gradientn(colours = rainbow(5))+
    facet_wrap(.~Source)+
    theme_cowplot()+
    theme(plot.title = element_text(hjust = 0.5))
}
PlotAllPropOcData("wt_d1_05")#looks cool, so let's keep going...

#now calculate the maximum frequency
propOcMaxDensity<-propOcHistogramData %>% 
    group_by(Sample, Distance, Source)%>% 
    mutate(MaxDensity = max(NormDensity)) %>% 
    mutate(DensityCh = ifelse(Density ==max(Density), 1, 0 )) %>% filter(DensityCh==1) %>% ungroup()#find max density, check where it matches
  propOcMaxDensityDoubles<-propOcMaxDensity %>% group_by(Sample,Distance, Source) %>% mutate(DoubledValues = sum(DensityCh)) %>% filter (DoubledValues>1)#this is just to find which values were repeated

  PlotMaxDensities <- function(sample) {
  ggplot()+
    geom_jitter(data = propOcMaxDensity %>% filter(Sample ==sample),aes(x=Value, y=Density,color = Distance),size=2)+
    labs(title ="Maximum Density")+
    scale_y_log10(breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
    facet_wrap( ~ Source, ncol = 2)+
    scale_color_gradientn(colours = rainbow(5))+
    #scale_shape_manual(values=c(0,1,2, 15,16,17))+
    theme_cowplot()+
    theme(plot.title = element_text(hjust = 0.5))
}
PlotMaxDensities("wt_d1_05")
  #maximum distribution isn't super representative, so for the distribution, I calculated the value at which 50% of the population is found

#Median distribution
getDeathCurve<-function(df){
  currentDensity = 0
  for (i in 1 : nrow(df)){
    addeddensity<-1-currentDensity
    df[i,9]<-addeddensity
    df[i,10]<-currentDensity
    currentDensity = currentDensity+df[i,8]
  }
  colnames(df)<-c("Value","Frequency","Density", "Distance", "Source","Sample", "count", "NormDensity", "Decay", "currentDens")
  df<-df %>% mutate (normDecay = (Decay - min(Decay)) / (max(Decay) - min(Decay)), DeltaDens = abs(Decay-currentDens))
  return(df)
  }
GetPercentiles<-function(input){
  df<-input %>% group_by(Sample, Distance, Source)
  yas<- group_split(df)
  mappedData<-map(yas, getDeathCurve)
  boundData<-bind_rows(mappedData)
return(boundData)}

#Calculate the cumulative density
testGetPercentiles<-GetPercentiles(propOcHistogramData %>% filter(Sample == "wt_d1_05"))#test case for sample wt_d1_05
propOcDensityData<-GetPercentiles(propOcHistogramData)#all data

#Calculate the value at half density
test50Percentile<-testGetPercentiles %>% group_by(Source, Sample, Distance) %>%filter(DeltaDens == min(DeltaDens))#test case for sample wt_d1_05
propOcMidDensity<-propOcDensityData %>% group_by(Source, Sample, Distance) %>%filter(DeltaDens == min(DeltaDens))#all data

PlotPercentiles <- function(df) {
  ggplot()+
    geom_point(data = df,aes(y=Value, color=normDecay,x = Distance, shape = Sample),size=2)+
    #geom_pointrange(data = df,aes(x = Distance,y=meanValue,ymax=meanValue+SdValue,ymin=meanValue-SdValue, color=Strain),size=2)+
    labs(title ="50 percentile Density")+
    #scale_y_log10(breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
    #scale_x_log10(breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
    facet_wrap( ~ Source, ncol = 2)+
    scale_color_gradientn(colours = rainbow(5))+
    theme_cowplot()+
    theme(plot.title = element_text(hjust = 0.5))
  }
PlotPercentiles(test50Percentile)#test case for sample wt_d1_05

#Clean up data for plotting and doing stats
##Recover conditions

PropOcDataFiltered1<-PropOcDataFiltered %>% group_by(Condition,TimePoint,SampleCode) %>% summarise(None = n()) %>% mutate(Sample = SampleCode)

propOcMidDensitylabeled <-merge(propOcMidDensity,PropOcDataFiltered1)

##Make them factors
propOcMidDensitylabeled$Condition <- factor(propOcMidDensitylabeled$Condition, levels = c("mono", "pawt","papqsL", "paphz", "wt", "pqsL", "phz"),labels = c('Sa mono', 'Pa wt mono','pqsL mono','phz mono','wt co', 'pqsL co', 'phz co'))
propOcMidDensitylabeled$TimePoint <- factor(propOcMidDensitylabeled$TimePoint, levels = c("d1", "d4"),labels = c('Day 1','Day 4'))

propOcMidDensitylabeled<-propOcMidDensitylabeled%>% mutate(Relation = recode(Source, "finalGG" = "Pa->Pa","finalRG" = "Sa->Pa","finalRR" = "Sa->Sa","finalGR" = "Pa->Sa"))

propOcMidDensitylabeled<-propOcMidDensitylabeled%>% mutate(Culture = recode(Condition, 'Sa mono' = "mono", 'Pa wt mono' = "mono",'pqsL mono'= "mono",'phz mono'= "mono",'wt co'= "co", 'pqsL co'= "co", 'phz co'= "co"))

propOcMidDensitylabeled<-propOcMidDensitylabeled%>% mutate(Strain = recode(Condition, 'Sa mono' = "Sa", 'Pa wt mono' = "wt",'pqsL mono'= "pqsL",'phz mono'= "phz",'wt co'= "wt", 'pqsL co'= "pqsL", 'phz co'= "phz"))

propOcMidDensityStats<-propOcMidDensitylabeled %>% ungroup() %>% group_by(Condition,Culture,Strain,TimePoint, Distance, Relation) %>% summarize(meanValue = mean(Value), sdValue = sd(Value), medianValue = median(Value))

ggplot()+#linear
    geom_point(data = propOcMidDensityStats %>% filter(Relation== "Pa->Pa"),aes(y=meanValue, x = Distance,color=Condition, shape = "Mean"),size=2)+
    geom_point(data = propOcMidDensityStats %>% filter(Relation== "Pa->Pa"),aes(y=medianValue, x = Distance,color=Condition,shape = "Median"),size=2)+
    labs(title ="mean 50 percentile Density")+
    #scale_y_log10(breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
    #scale_x_log10(breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
    facet_grid(Relation ~ TimePoint)+
    #scale_color_gradientn(colours = rainbow(5))+
    #scale_shape_manual(values=c(0,1,2, 15,16,17))+
    scale_color_brewer(palette = "Set1")+
    theme_cowplot()+
    theme(plot.title = element_text(hjust = 0.5))

ggplot()+#linear
    geom_point(data = propOcMidDensityStats %>% filter(Relation== "Sa->Sa"),aes(y=meanValue, x = Distance,color=Culture, shape = "Mean"),size=2)+
    geom_point(data = propOcMidDensityStats %>% filter(Relation== "Sa->Sa"),aes(y=medianValue, x = Distance,color=Culture,shape = "Median"),size=2)+
    labs(title ="mean 50 percentile Density")+
    #scale_y_log10(breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
    #scale_x_log10(breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
    facet_grid(Strain ~ TimePoint)+
    #scale_color_gradientn(colours = rainbow(5))+
    #scale_shape_manual(values=c(0,1,2, 15,16,17))+
    scale_color_brewer(palette = "Set1")+
    theme_cowplot()+
    theme(plot.title = element_text(hjust = 0.5))

@@

```{r Original Whole PropOc frequency functions from mBio Paper -DONE}
GetAllHistPropOc <- function(df, timepoint){
  data.GG<-GetHistPropOc(df, timepoint, "finalGG")
  data.RG<-GetHistPropOc(df, timepoint, "finalRG")
  data.RR<-GetHistPropOc(df, timepoint, "finalRR")
  data.GR<-GetHistPropOc(df, timepoint, "finalGR")
  allData<- bind_rows(data.GG,data.RR,data.RG,data.GR)
return(allData)
}

@@

```{r Whole PropOc frequency Figures -DONE}
PlotAllPropOcData <- function(df, relation ) {
  ggplot()+ 
    geom_point(data = df %>% filter(Source == relation),aes(x=Value,y=Frequency, color = Distance),size=2)+
    scale_y_log10( breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
    #scale_x_log10( breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
    #labs(title =paste( relation, timepoint))+
    #scale_color_viridis(option = "D")+
    scale_color_gradientn(colours = rainbow(5))+
    xlim(0,1)+
    theme_cowplot()+
    theme(plot.title = element_text(hjust = 0.5))
  #name<-paste0(relation, ".hour", timepoint,".png")
  #ggsave(paste0(name),plot = plot, width = 17, height = 10)
}

@@

```{r Whole PropOc Data wrangling -DONE}
#So, I think the first thing to do would be to get a "mode", or the highest value for frequency of proportional occupancy per distance.
#at this point I can see at least if the zone of interest is the same for every sample.

@@

```{r Max Density Figures -DONE}
PlotMaxDensities <- function(df) {
  ggplot()+
    geom_jitter(data = df,aes(y=Value, color=Density,x = Distance, shape = Sample),size=2)+
    labs(title ="Maximum Density")+
    scale_y_log10(breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
    #scale_x_log10(breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
    facet_wrap( ~ Source, ncol = 2)+
    scale_color_gradientn(colours = rainbow(5))+
    scale_shape_manual(values=c(0,1,2, 15,16,17))+
    theme_cowplot()+
    theme(plot.title = element_text(hjust = 0.5))
}
PlotMaxDensities(allDensities)
PlotMaxDensities(allDensitiesFunctions %>% filter(Source=="finalRG"))
PlotMaxDensities(allDensitiesLog)
PlotMaxDensities(allDensitiesLog2)
```

#Calculating 50 percentile density.
```{r death curves Functions and data -DONE}
getDeathCurve<-function(df){
  totalFrequency = sum(df$Frequency)
  currentFrequency = 0
  for (i in 1 : nrow(df)){
    addedFrequency<-totalFrequency-currentFrequency
    df[i,6]<-addedFrequency
    currentFrequency = currentFrequency+df[i,2]
  }
  colnames(df)<-c("Value","Frequency","Density", "Distance", "Source","Decay")
  df<-df %>% mutate (normDecay = 100*(Decay - min(Decay)) / (max(Decay) - min(Decay)))
  return(df)
  }
processData<-function(df){
  allData<-df %>% group_by(Distance, Source)
  yas<- group_split(allData)
  mappedData<-map(yas, getDeathCurve)
  boundData<-bind_rows(mappedData)
}
GetPercentiles<-function(histograms){
  histogramNames<- c("wt1.1","wt2.1","wt3.1","mut1.1","mut2.1","mut3.1")
  mappedDensities<-map(histograms,processData)
  namedMappedDensities<-map2(mappedDensities, histogramNames, ~.x %>% mutate(Sample = .y))
  allDensities<-bind_rows(namedMappedDensities)
  allDensities<-allDensities %>% ungroup() %>% 
    mutate(Strain = recode(allDensities$Sample, wt1.1="wt",wt2.1="wt",wt3.1="wt",mut1.1="mut",mut2.1="mut",mut3.1="mut"))
return(allDensities)}

@@

allDeathCurvesLog2midAbsStats<-allDeathCurvesLog2midAbsStats%>% mutate(Relation = recode(Source, "finalGG" = "Pa->Pa","finalRG" = "Sa->Pa","finalRR" = "Sa->Sa","finalGR" = "Pa->Sa"))
ggplot()+#log transform
  geom_pointrange(data = allDeathCurvesLog2midAbsStats,aes(x = Distance,y=meanLogValue,ymax=meanLogValue+sdLogValue,ymin=meanLogValue-sdLogValue, color=Strain),size=.5)+
  facet_wrap( ~ Relation, ncol = 2)+
  scale_color_grey(name = "Strain", labels = c( "HQNO-","Wild Type"))+  
  theme_cowplot()+
  theme(plot.title = element_text(hjust = 0.5))
```

#Enrichment (distance at highest proportional occupancy) 
```{r Enrichment}
#find the max proportional occupancy value from the 50 percentile

allDeathCurvesLog2midAbsEnrichment<- allDeathCurvesLog2midAbs %>% group_by(Sample, Source)%>%
  select(Value, Distance, Source,Sample, Strain, Percentile50) %>% mutate(Enrichment = max(Value)) %>%
  mutate(EnrichmentCh = ifelse(Enrichment == Value, 1, 0 )) %>% filter(EnrichmentCh==1) %>% 
  mutate(DoubledValues = sum(EnrichmentCh)) %>% ungroup()#find max

@@

#That looks like a lot of the values are just at 0.5 distance, which I dont really care, I can make another argument about direct contact, so I'll filter those out...
allDeathCurvesLog2midAbsEnrichment2<-allDeathCurvesLog2midAbs %>% filter(!Distance ==0.5)%>% 
  group_by(Sample, Source) %>% select(Value, Distance, Source,Sample, Strain, Percentile50) %>% mutate(Enrichment = max(Value)) %>%
  mutate(EnrichmentCh = ifelse(Enrichment == Value, 1, 0 )) %>% filter(EnrichmentCh==1) %>% mutate(DoubledValues = sum(EnrichmentCh)) %>% ungroup()#find max
